Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Added URL footnotes for detectors
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1147 ccdd05d5-56c1-461a-bf98-85f6876523b4

In October 2010, \LIGO{} completed its sixth science run
(S6) and Virgo completed its third science run (VSR3).  While both
\LIGO{} detectors and Virgo were operating, several all-sky detection
pipelines operated in a low-latency configuration to send astronomical alerts,
namely \textsc{mbta}, Coherent WaveBurst, and
Omega \citep{HugheyGWPAW2011, S6lowlatency}. The S6 analyses
achieved latencies of 30--60 minutes, which were dominated by a human vetting
process. Candidates were sent for \EM{} followup to several
telescopes; Swift, \textsc{rotse}, \textsc{tarot}, and Zadko \citep{kanner2008,
HugheyGWPAW2011} took images of likely sky locations.  \textsc{mbta} achieved
the best \GW{} trigger-generation latencies of 2--5 minutes.  We
assume that in the advanced detector era the vetting process will be automated,
so current \GW{} search methodology and telescope actuation would
dominate latency.

>>>>

In October 2010, \LIGO{}\footnote{\url{http://www.ligo.org/}} completed its sixth science run
(S6) and Virgo\footnote{\url{http://www.ego-gw.it/}} completed its third science run (VSR3).
While both \LIGO{} detectors and Virgo were operating, several all-sky detection
pipelines operated in a low-latency configuration to send astronomical alerts,
namely \textsc{mbta}, Coherent WaveBurst, and
Omega \citep{HugheyGWPAW2011, S6lowlatency}. The S6 analyses
achieved latencies of 30--60 minutes, which were dominated by a human vetting
process. Candidates were sent for \EM{} followup to several
telescopes; Swift, \textsc{rotse}, \textsc{tarot}, and Zadko \citep{kanner2008,
HugheyGWPAW2011} took images of likely sky locations.  \textsc{mbta} achieved
the best \GW{} trigger-generation latencies of 2--5 minutes.  We
assume that in the advanced detector era the vetting process will be automated,
so current \GW{} search methodology and telescope actuation would
dominate latency.
